%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
% \usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }

% optional 
% \clearpage

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}

    \Huge{Gaurav Gorane} \\[14pt]
    \href{https://github.com/gauravgorane}{\raisebox{-0.05\height}\faGithub\ gauravgorane} \ $|$ \ 
    \href{https://linkedin.com/in/gauravgorane/}{\raisebox{-0.05\height}\faLinkedin\ gauravgorane} \ $|$ \ 
    \href{https://gauravgorane.github.io/}{\raisebox{-0.05\height}\faGlobe \ gauravgorane.github.io} \ $|$ \ 
    \href{mailto:gauravvg11@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ gauravvg11@gmail.com} \ $|$ \ 
    \href{tel:+918862028027}{\raisebox{-0.05\height}\faMobile \ +91 8862-0280-27} \\
    
\end{tabularx}

%----------------------------------------------------------------------------------------
% Summary
%----------------------------------------------------------------------------------------
\section{Summary}
I’m a Computer Engineering student with a strong passion for Web Development. I enjoy creating engaging, and user-friendly digital experiences. My interests lie in building projects that solve real-world problems and improve how users interact with technology. I’m always eager to learn new tools and collaborate on solutions that make a meaningful impact.

%----------------------------------------------------------------------------------------
% Projects
%----------------------------------------------------------------------------------------
\section{Projects}

    % \textbf{Some Project} & \hfill \href{https://some-link.com}{Link to Demo} \\[3.75pt]
    % \multicolumn{2}{@{}X@{}}{long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width}  \\

    \begin{joblong}
        {\href{https://github.com/gauravgorane/Shopping_cart}{Shopping Cart \faExternalLink*} \normalfont{\textit{[JavaScript, Tailwind CSS, Firebase, PWA]}}}{June 2024}
        \item Built a real-time shopping list app using Firebase Realtime Database for data storage and sync. 
        \item Implemented add/delete functionality, accessibility fixes, and responsive design for mobile users.
        \item Converted the web app into a Progressive Web App (PWA) with offline support and home screen installability.
    \end{joblong}

    \begin{joblong}
        {\href{https://github.com/gauravgorane/React_mini_projects}{React Mini Projects \faExternalLink*} \normalfont{\textit{[React, React Hooks, Components]}}}{June 2024}
        \item Built interactive mini apps (e.g., Meme Generator, Tenzies Game, ...) while learning modern React fundamentals.
        \item Practiced JSX, props, state, event handling, side effects, controlled components, and accessibility.
        \item Strengthened understanding of React architecture through hands-on capstone projects and challenge-based learning.
    \end{joblong}

    \begin{joblong}
        {\href{https://github.com/gauravgorane/profile-map-app}{Profile Map App \faExternalLink*} \normalfont{\textit{[React, React Router, Leaflet, Tailwind CSS]}}}{June 2024}
        \item Created an interactive map-based profile viewer app to visualize location data.
        \item Used Leaflet.js to plot and interact with user data on maps.
    \end{joblong}

    \begin{joblong}
        {\href{https://github.com/gauravgorane/Frontend_mentor_js}{Frontend Mentor JS \faExternalLink*} \normalfont{\textit{[JavaScript, DOM, Web Components]}}}{June 2024}
        \item Built interactive solutions to JavaScript-focused challenges from Frontend Mentor.
        \item Strengthened understanding of core JS concepts and DOM manipulation.
    \end{joblong}

    \begin{joblong}
        {\href{https://github.com/gauravgorane/Frontend_Mentor}{Frontend Mentor Challenges \faExternalLink*} \normalfont{\textit{[HTML, CSS, Responsive Design]}}}{Aug 2024}
        \item Solved 20+ real-world UI challenges focusing on responsive design and accessibility.
        \item Improved skills in HTML, CSS (Flexbox \& Grid), and pixel-perfect layout implementation. 
    \end{joblong}

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Experience}

    % \begin{jobshort}{Designation}{Jan 2021 - present}
    % long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width
    % \end{jobshort}
    
    % \begin{joblong}{Designation}{Mar 2019 - Jan 2021}
    %     \item long long line of blah blah that will wrap when the table fills the column width
    %     \item again, long long line of blah blah that will wrap when the table fills the column width but this time even more long long line of blah blah. again, long long line of blah blah that will wrap when the table fills the column width but this time even more long long line of blah blah
    % \end{joblong}

    \begin{joblong}{GDGoC WOW – Google Developer Group Community - \normalfont{\textit{Design Team Member}}}{Feb 2024 - Apr 2024}
        \item Worked on website UI/UX design using Figma.
        \item Designed standees, posters, and other promotional materials for community events.
        \item Collaborated with the design team to maintain brand consistency across various assets.
    \end{joblong}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	

    % 2030 - present & PhD (Subject) at \textbf{University} \hfill \normalsize (GPA: 4.0/4.0) \\
    % 2023 - 2027 & Bachelor's Degree at \textbf{College} \hfill (GPA: 4.0/4.0) \\ 
    % 2022 & Class 12th Some Board \hfill  (Grades) \\
    % 2021 & Class 10th Some Board \hfill  (Grades) \\

    \textbf{Dr. D. Y. Patil Institute of Technology, Pimpri, Pune - 18} & \hfill Sep 2021 - June 2025 \\ \vspace*{2mm}
    B.E. Computer Engineering. 8.88 CGPA \\ 
    
    \textbf{Amrita Vidyalayam \& Junior College, Nigdi, Pune - 44} & \hfill Aug 2019 - June 2021 \\ \vspace*{2mm}
    H.S.C. 86.67\% \\ 
    
    \textbf{M S S HighSchool, Chinchwad , Pune - 17} & \hfill May 2019 \\ \vspace*{2mm}
    S.S.C. 91.60\% \\

\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Languages} &  \normalsize{C, C++, Python, HTML, CSS, JavaScript}\\
\textbf{Databases} &  \normalsize{MySQL, SQLite, MongoDB, Firestore}\\
\textbf{Frameworks}  &  \normalsize{React, Bootstrap, Tkinter}\\
\textbf{Tools}  &  \normalsize{Git, GitHub, Google Cloud Platform, Postman, Figma, Canva, LaTeX, Notion}\\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	VOLUNTEERING
%----------------------------------------------------------------------------------------
\section{Volunteering}

\begin{tabularx}{\linewidth}{@{}l X@{}}	

\textbf{Head of Operations, Google Developer Groups $|$ DPU-DIT} & \hfill 
2024-25 \\ \vspace*{1mm}
Organized zone-level tech events and secured major sponsorships, overseeing smooth execution. \\

\textbf{Tech Editor, Google Developer Student Clubs DIT, Pune} & \hfill 
2023-24 \\ \vspace*{1mm}
Designed digital assets and collaborated across tech and non-tech teams for various initiatives. \\

\textbf{Social Media Coordinator, National Service Scheme} & \hfill 
2022-24 \\ \vspace*{1mm}
Managed social media outreach and partnered with organizations to promote social causes. \\ 

\textbf{Student Coordinator, Entrepreneurship Development and Start-up Innovation Cell} & \hfill 
2022-23 \\ \vspace*{1mm}
Led last-minute coordination with entrepreneurs to ensure impactful discussions and events. \\ 

\end{tabularx}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------
\section{Certifications \& Achievements}

\textbf{Copyright – A Distributed Architecture Quiz App} \\
- Received a government-registered copyright for developing a distributed architecture-based quiz application. \\[1ex]
\textbf{Responsive Web Design (freeCodeCamp)} \\
- Learned fundamentals of Web Design and Development. \\[1ex]
\textbf{JavaScript Algorithms \& Data Structures (freeCodeCamp)} \\
- Completed a hands-on course covering core JavaScript concepts. \\[1ex]
\textbf{Cisco Networking Basics} \\
- Gained understanding of Computer Networks. \\[1ex]
\textbf{Google Cloud 30 Days Challenge} \\
- Explored various Google Cloud services and completed the Career Practitioner program. \\[1ex]

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
% \section{Publications}
% \begin{refsection}[citations.bib]
% \nocite{*}
% \printbibliography[heading=none]
% \end{refsection}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
